Supplemental Material - _metagenomeFeatures_: An R package for working with 16S rRNA reference databases and marker-gene survey feature data.

### 2019-02-02 inst/manuscript/manuscript_supplemental.Rmd
fixed session info bug for submission

# Session Information {#sessionInfo}
## System Information
```{r warning = FALSE}
s_info <- devtools::session_info(include_base = FALSE)
pander::pander(s_info$platform)
```

## Package Versions
```{r}
s_info$packages %>% filter(`*` == "*") %>% select(-`*`) %>%
    knitr::kable(booktabs = TRUE)
```

>>>>

# Session Information {#sessionInfo}
## System Information
```{r}
sessioninfo::platform_info()
```

## Package Versions
```{r}
sessioninfo::package_info() %>% 
  filter(attached == TRUE) %>% 
  select(package, loadedversion, source) %>% 
    knitr::kable(booktabs = TRUE)
```
